% This setup has you inputting the bibliography manually, this can be done away with by using
% BiBTeX, but that has not been used/implemented in this template, so, you are free/encouraged
% to use it to make your life much easier, but we are still in the process of integrating BiBTeX
\begin{thebibliography}{100}
\pagestyle{plain}
\bibitem{book:guide}
The~Editorial Office of the Graduate School,
\newblock \emph{Guide for Preparing Theses and Dissertations},
\newblock The University of Florida, \emph{Revised} 1998.

\bibitem{abdulra.m.sheikh.auh.ea:94}
M.~Abdulrahan, A.~U.~H. Sheikh, and D.~D. Falconer,
\newblock ``Decision feedback equalization for {CDMA} in indoor wireless
  communications,''
\newblock \emph{IEEE Journal on Selected Areas in Communications}, vol. 12, no.
  4, pp. 698--706, May 1994.

\bibitem{barbosa.an.miller.sl:98}
A.~N. Barbosa and S.~L. Miller,
\newblock ``Adaptive detection of {DS/CDMA} signals in fading channels,''
\newblock \emph{IEEE Transactions on Communications}, vol. 46, no. 1, pp.
  115--124, Jan. 1998.

\bibitem{barghou.rt.stuber.gl:92}
R.~T. Barghouthi and G.~L. St{\"u}ber,
\newblock ``Sequence acquisition techniques for {CDMA} systems employing
  {Kasami} sequences,''
\newblock in \emph{Proceedings~IEEE Military Communications Conference}, San
  Diego, CA, 1992, vol.~2, pp. 633--637.

\bibitem{barghou.rt.stuber.gl:94}
R.~T. Barghouthi and G.~L. St{\"u}ber,
\newblock ``Rapid sequence acquisition for {DS/CDMA} systems employing {Kasami}
  sequences,''
\newblock \emph{IEEE Transactions on Communications}, vol. 42, no. 2/3/4, pp.
  1957--1968, Feb./Mar./Apr. 1994.

\bibitem{bensley.se.aazhang.b:96}
S.~E. Bensley and B.~Aazhang,
\newblock ``Subspace-based channel estimation for code division multiple access
  communication systems,''
\newblock \emph{IEEE Transactions on Communications}, vol. 44, no. 8, pp.
  1009--1020, Aug. 1996.

\bibitem{bensley.se.aazhang.b:98}
S.~E. Bensley and B.~Aazhang,
\newblock ``{Maximum}-{Likelihood} synchronization of a single user for
  code-division multiple-access communication systems,''
\newblock \emph{IEEE Transactions on Communications}, vol. 46, no. 3, pp.
  392--399, Mar. 1998.

\bibitem{bershad.nj.qu.lz:89}
N.~J. Bershad and L.~Z. Qu,
\newblock ``On the probability density function of the {LMS} adaptive filter
  weights,''
\newblock \emph{IEEE Transactions on Acoustics, Speech and Signal Processing},
  vol. 37, no. 1, pp. 43--56, Jan. 1989.

\bibitem{braun.wr:97}
W.~R. Braun,
\newblock ``{PN} acquisition and tracking performance in {DS/CDMA} systems with
  symbol-length spreading sequences,''
\newblock \emph{IEEE Transactions on Communications}, vol. 45, no. 12, pp.
  1595--1601, Dec. 1997.

\bibitem{buehrer.rm.kaul.a.ea:96}
R.~M. Buehrer, A.~Kaul, S.~Striglis, and B.~D. Woerner,
\newblock ``Analysis of {DS-CDMA} parallel interference cancellation with phase
  and timing errors,''
\newblock \emph{IEEE Journal on Selected Areas in Communications}, vol. 14, no.
  8, pp. 1522--1535, Oct. 1996.

\bibitem{buehrer.rm.woerner.bd:95}
R.~M. Buehrer and B.~D. Woerner,
\newblock ``Analysis of adaptive multistage interference cancellation for
  {CDMA} using an improved {Gaussian} approximation,''
\newblock in \emph{Proceedings~IEEE Military Communications Conference}, San
  Diego, CA, 1995, vol.~3, pp. 1195--1199.

\bibitem{chang.rw.sriniva.r:80}
R.~W. Chang and R.~Srinivasagopalan,
\newblock ``Carrier recovery for data communication systems with adaptive
  equalization,''
\newblock \emph{IEEE Transactions on Communications}, vol. COM--28, no. 8, pp.
  1142--1153, Aug. 1980.

\bibitem{clarke.rh:68}
R.~H. Clarke,
\newblock ``A statistical theory of mobile-radio reception,''
\newblock \emph{The Bell System Technical Journal}, vol. 47, no. 6, pp.
  957--1000, July-Aug. 1968.

\bibitem{couch-ii.lw:97}
L.~W. Couch~II,
\newblock \emph{Digital and Analog Communication Systems},
\newblock Prentice-Hall, 5th edition, 1997.

\bibitem{davies.rb:73}
R.~B. Davies,
\newblock ``Numerical inversion of a characteristic function,''
\newblock \emph{Biometrika}, vol. 60, no. 2, pp. 415--417, 1973.

\bibitem{davies.rb:80}
R.~B. Davies,
\newblock ``The distribution of a linear combination of $\chi^2$ random
  variables,''
\newblock \emph{Applied Statistics}, vol. 29, no. 3, pp. 323--333, 1980.

\bibitem{douglas.sc.meng.thy:92}
S.~C. Douglas and T.~H.-Y. Meng,
\newblock ``Exact expectation analysis of the {LMS} adaptive filter without the
  independence assumption,''
\newblock in \emph{Proceedings~IEEE International Conference on Acoustics,
  Speech and Signal Processing}, San Francisco, CA, 1992, vol.~4, pp. 61--64.

\bibitem{douglas.sc:93}
S.~C. Douglas,
\newblock ``Exact expectation analysis of the {LMS} adaptive filter for
  correlated {Gaussian} input data,''
\newblock in \emph{Proceedings~IEEE International Conference on Acoustics,
  Speech and Signal Processing}, Minneapolis, MN, 1993, vol.~3, pp. 519--522.

\end{thebibliography}
